Earth_microbiome_MS

### 2019-07-15 Earth_microbiome_MS.Rmd
updated

#Read phyloseq object
```{r Taxonomic filtering}
#Methods obtained from Callahan et al.

>>>>

#Read phyloseq object
```{r Phyloseq object - first read}
#Methods from MRD microbiome file
#Print phyloseq object to check its component parts
print(githubdata_phyloseq)

#Check sparsity of physeq data
kable(head(tax_table(githubdata_phyloseq)))
tax_table(githubdata_phyloseq)

#summarize_phyloseq(githubdata_phyloseq)
#The above code ran unsuccessfully due to the fact that the data does not include sample data
```

```{r Taxonomic filtering}
#Methods obtained from Callahan et al.
